\begin{thebibliography}{150}

    % Set Reference ID carefully, do not use replication
    \bibitem {1} L. Fei-Fei, R. Fergus, and P. Perona. Learning generative visual
models from few training examples: An incremental bayesian
approach tested on 101 object categories. Computer Vision and
Image Understanding, 106(1):59–70, 2007.

\bibitem {2} J. Deng, W. Dong, R. Socher, L.-J. Li, K. Li, and L. FeiFei. Imagenet: A large-scale hierarchical image database. In
Computer Vision and Pattern Recognition, pages 248–255, 2009.

\bibitem {3} D. G. Lowe. Distinctive image features from scale-invariant
keypoints. International Journal of Computer Vision, 60(2):91–
110, 2004.

\bibitem {4} S. Lazebnik, C. Schmid, and J. Ponce. Beyond bags of features:
Spatial pyramid matching for recognizing natural scene categories. In Computer Vision and Pattern Recognition, volume 2,
pages 2169–2178, 2006.

\bibitem {5} J. Wang, J. Yang, K. Yu, F. Lv, T. Huang, and Y. Gong. Localityconstrained linear coding for image classification. In Computer
Vision and Pattern Recognition, pages 3360–3367, 2010.

\bibitem {6} C.-C. Chang and C.-J. Lin. Libsvm: a library for support
vector machines. ACM Trans. Intelligent Systems and Technology,
2(3):27, 2011.

\bibitem {7}  L. Breiman. Random forests. Machine learning, 45(1):5–32, 2001.

\bibitem {8} Y. LeCun, B. Boser, J. Denker, D. Henderson, R. Howard,
W. Hubbard, and L. Jackel. Handwritten digit recognition with
a back-propagation network. In Neural Information Processing
Systems, 1990.

\bibitem {9} K. Jarrett, K. Kavukcuoglu, M. Ranzato, and Y. LeCun. What
is the best multi-stage architecture for object recognition? In
International Conference on Computer Vision, pages 2146–2153,
2009.

\bibitem {10} A. Krizhevsky, I. Sutskever, and G. Hinton. Imagenet classification with deep convolutional neural networks. In Neural
Information Processing Systems, pages 1106–1114, 2012.

\bibitem {11} W. Ouyang and X. Wang. Joint deep learning for pedestrian
detection. In International Conference on Computer Vision, pages
2056–2063, 2013.

\bibitem {12} F. Perronnin, J. Sanchez, and T. Mensink. Improving the ´
fisher kernel for large-scale image classification. In European
Conference on Computer Vision, pages 143–156, 2010.

\bibitem {13} Q. Chen, Z. Song, Y. Hua, Z. Huang, and S. Yan. Hierarchical
matching with side information for image classification. In
Computer Vision and Pattern Recognition, pages 3426–3433, 2012.

\bibitem {14} J. Dong, W. Xia, Q. Chen, J. Feng, Z. Huang, and S. Yan.
Subcategory-aware object classification. In Computer Vision and
Pattern Recognition, pages 827–834, 2013.

\bibitem {15} Alexe, B., Deselares, T. and Ferrari.
 Measuring the objectness of image windows. V. PAMI 2012.

\bibitem {16} R. R. Uijlings, Koen E. A. van de Sande, Theo Gevers, Arnold W. M. Smeulders. 
Selective Search for Object Recognition, Jasper  International Journal of Computer Vision, Volume 104 (2), page 154-171, 2013.

\bibitem {17} Dataset of CIFAR-10 https://www.cs.toronto.edu/~kriz/cifar.html.

\bibitem {18} H. Harzallah, F. Jurie, and C. Schmid. Combining efficient
object localization and image classification. In Computer Vision
and Pattern Recognition, pages 237–244, 2009.

\bibitem {19} Y. Gong, Y. Jia, T. K. leung, A. Toshev, and S. Ioffe. deep
convolutional ranking for multi label image annotation. In
International Conference on Learning Representations, 2014.

\bibitem {20} N. Dalal and B. Triggs. Histograms of oriented gradients for
human detection. In Computer Vision and Pattern Recognition,
volume 1, pages 886–893, 2005.

\bibitem {21} T. Ojala, M. Pietikainen, and D. Harwood. A comparative 
study of texture measures with classification based on featured
distributions. Pattern recognition, 29(1):51–59, 1996.

\bibitem {22} N. M. Nasrabadi and R. A. King. Image coding using vector quantization: A review. IEEE Trans. Communications, 36(8):957–
971, 1988.

\bibitem {23} P. Hedelin and J. Skoglund. Vector quantization based on
gaussian mixture models. IEEE Trans. Speech and Audio Processing, 8(4):385–401, 2000.

\bibitem{24} D. Comaniciu and P. Meer. Mean shift: a robust approach
toward feature space analysis. TPAMI, 24:603–619, 2002.

\bibitem{25} P. F. Felzenszwalb and D. P. Huttenlocher. Efficient GraphBased Image Segmentation. IJCV, 59:167–181, 2004. 

\bibitem{26} Sergey Ioffe, Christian Szegedy.
 Batch Normalization: Accelerating Deep Network Training by Reducing
Internal Covariate Shift.

\end{thebibliography}
